\textbf{ Discovery of a disrupting open cluster far into the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2019-05-24 ms.tex
more updates

\newcommand{\clage}{\ensuremath{116~\textrm{Myr}}}
\newcommand{\clfeh}{\ensuremath{-1.14}}
\newcommand{\cldist}{\ensuremath{28.7~\textrm{kpc}}}

\newcommand{\clageerr}{\ensuremath{116 \pm 7~\textrm{Myr}}}
\newcommand{\clfeherr}{\ensuremath{-1.14 \pm 0.05}}
\newcommand{\cldisterr}{\ensuremath{28.7 \pm 0.4~\textrm{kpc}}}
\newcommand{\claverr}{\ensuremath{0.21 \pm 0.02}}

@@

The origin and formation of these LA features is still uncertain.
Initial studies of the LA argued that the features closest to the \lmcsmc\ can be traced back to the SMC \citep{Putman:1998}, but outer features of the LMC appear to lead directly into the LA I feature \citep{Nidever:2008}.
Recent chemical abundance measurements along several sight-lines passing through the LA again support an SMC origin for the gas \citep{Fox:2018, Richter:2018}.
Whatever the origin of the LA gas, it is clear that tidal stripping by the Milky Way is required to form the LA \citep{Nidever:2008, Besla:2012}.
However, the LA features deviate from the predicted orbit of the \lmcsmc, implying that ram pressure or interactions the outer Milky Way disk (from the recent disk plane passage) may have removed orbital energy from the LA gas \citep[e.g.,][]{Bekki:2008}.

@@

\changes{The instrumental photometry (i.e., $-2.5\log(\texttm{ADU}~\textrm{sec}^{-1}$) was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for g- and i-band and with SkyMapper \citep{Wolf:2018} for the u-band observations.
We use a robust linear fit to cross-matched sources (that appear in both PS1 and our observations) to obtain a zero-point and color-term (no color-term was needed for u-band) to derive color transformations relating our instrumental DECam photometry to calibrated SkyMapper u- and PS1 grizy photometry (see \tablename~\ref{tbl:transphot} for the derived transformation coefficients).
We apply this color transformation to put our photometry on the SkyMapper/PS1 system, enabling us to treat this photometry as if it were PS1/SkyMapper photometry in the isochrone modeling.
The robust RMS around the linear fit is 0.028 mag for g- and i-band and 0.164 mag for the u-band; We adopt these RMS values as systematic errors that are added in quadrature to the photometric uncertainties for individual sources in the modeling described below.
The larger scatter in u-band---much larger than the uncertainty in the individual photometry---is due to the large differences in the DECam and SkyMapper u-band passbands.}

@@

\begin{center}
\begin{deluxetable}{ccrrr}
\tablecaption{DECam Photometric Transformation Equations\label{tbl:transphot}}
\tablecolumns{5}
\tablewidth{400pt}
\tablehead{
\colhead{Band} & \colhead{Color} & \colhead{Zero-point term} & \colhead{Color term}
}
\startdata
% $u$  &  \nodata & $2.178 \pm  0.016$ &     \nodata \\
% $g$  & $g-r$ & $-0.05287 \pm  0.0068$  &     $-0.03494 \pm 0.0051$ \\
% $i$   &  $i-z$ & $-0.24665 \pm 0.0011$ &     $-0.07379 \pm 0.00069$
$u$  &  \nodata & $27.178 \pm  0.016$ &     \nodata \\
$g$  & $g-r$ & $24.9471 \pm  0.0068$  &     $-0.03494 \pm 0.0051$ \\
$i$   &  $i-z$ & $24.7534 \pm 0.0011$ &     $-0.07379 \pm 0.0007$
\enddata
\end{deluxetable}
\end{center}

@@

We therefore take a closer look at the \hi gas in the vicinity of \clustername\ to assess its possible relation to the MS.
While no bulk metallicity measurements exist for the LA gas, recent measurements of oxygen and silicon abundances ($\[O/H\] \sim -1$) suggest that the gas has a comparable abundance pattern to the SMC gas \citep{Fox:2018, Richter:2018}.
If \clustername\ formed from this gas, we would then expect that the stellar metallicity should be similar to young stars in the SMC.
In the outskirts of the SMC, the metallicity distribution of the youngest stars ($\textrm{age} < 2~\textrm{Gyr}$) has a peak around $\feh \sim -1$ and a spread of $\sigma_{\feh} \sim 0.2~\textrm{dex}$, which at least means that the metallicity of \clustername\ ($\feh \approx -1.1$) is consistent with young SMC stars \citep{Dobbie:2014}.

>>>>

\newcommand{\clage}{\ensuremath{117~\textrm{Myr}}}
\newcommand{\clfeh}{\ensuremath{-1.14}}
\newcommand{\cldist}{\ensuremath{28.7~\textrm{kpc}}}

\newcommand{\clageerr}{\ensuremath{117 \pm 23~\textrm{Myr}}}
\newcommand{\clfeherr}{\ensuremath{-1.14 \pm 0.05}}
\newcommand{\cldisterr}{\ensuremath{28.7 \pm 0.5~\textrm{kpc}}}
\newcommand{\claverr}{\ensuremath{0.205 \pm 0.011}}

@@

The origin and formation of these LA features is still uncertain.
Initial studies of the LA argued that the features closest to the \lmcsmc\ can be traced back to the SMC \citep{Putman:1998}, but outer features of the LMC appear to lead directly into the LA I feature \citep{Nidever:2008}.
Recent chemical abundance measurements along several sight-lines passing through the LA again support an SMC origin for the gas \citep{Fox:2013, Fox:2018, Richter:2018}.
Whatever the origin of the LA gas, it is clear that tidal stripping by the Milky Way is required to form the LA \citep{Nidever:2008, Besla:2012}.
However, the LA features deviate from the predicted orbit of the \lmcsmc, implying that ram pressure or interactions the outer Milky Way disk (from the recent disk plane passage) may have removed orbital energy from the LA gas \citep[e.g.,][]{Bekki:2008}.

@@

\changes{The instrumental photometry (i.e., $-2.5\log(\textrm{ADU}~\textrm{sec}^{-1}$) was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for g- and i-band and with SkyMapper \citep{Wolf:2018} for the u-band observations.
We use a robust linear fit to cross-matched sources (that appear in both PS1 and our observations) to obtain a zero-point and color-term (no color-term was needed for the u-band) to derive color transformations relating our instrumental DECam photometry to calibrated PS1 grizy and SkyMapper u-band photometry (see \tablename~\ref{tbl:transphot} for the derived transformation coefficients).
We apply this color transformation to the instrumental photometry---including a constant 25 mag offset applied by DAOPHOT and an offset by $2.5\,\log{t_{\rm exp}}$ given the exposure time $t_{\rm exp}$---to put our photometry on the PS1/DECam system.
This calibration enables us to treat the photometry as if it were PS1 (g- and i-band) and DECam (u-band) photometry in the isochrone modeling described below.
The robust RMS around the linear fit is 0.028 mag for g- and i-band and 0.164 mag for the u-band; We adopt these RMS values as systematic errors that are added in quadrature to the photometric uncertainties for individual sources in the modeling described below.
The larger scatter in u-band---larger than the uncertainty in the individual photometry---is due to the significant differences between the DECam and SkyMapper u-band passbands.
}

@@

\begin{center}
\begin{deluxetable}{ccrrr}
\tablecaption{DECam Photometric Transformation\label{tbl:transphot}}
\tablecolumns{5}
\tablewidth{400pt}
\tablehead{
\colhead{Band} & \colhead{Color} & \colhead{Zero-point term} & \colhead{Color term}
}
\startdata
% $u$  &  \nodata & $2.178 \pm  0.016$ &     \nodata \\
% $g$  & $g-r$ & $-0.05287 \pm  0.0068$  &     $-0.03494 \pm 0.0051$ \\
% $i$   &  $i-z$ & $-0.24665 \pm 0.0011$ &     $-0.07379 \pm 0.00069$
$u_{\rm DECam}$  &  \nodata & $27.178 \pm  0.016$ &     \nodata \\
$g_{\rm PS1}$  & $g_{\rm inst.}-i_{\rm inst.}$ & $24.9471 \pm  0.0068$  &     $-0.03494 \pm 0.0051$ \\
$i_{\rm PS1}$   &  $g_{\rm inst.}-i_{\rm inst.}$ & $24.7534 \pm 0.0011$ &     $-0.07379 \pm 0.0007$
\enddata
\end{deluxetable}
\end{center}

@@

We therefore take a closer look at the \hi gas in the vicinity of \clustername\ to assess its possible relation to the MS.
While no bulk metallicity measurements exist for the LA gas, recent measurements of oxygen and silicon abundances ($[\textrm{O}/\textrm{H}] \sim -1$) suggest that the gas has a comparable abundance pattern to the SMC gas \citep{Fox:2013, Fox:2018, Richter:2018}.
If \clustername\ formed from this gas, we would then expect that the stellar metallicity should be similar to young stars in the SMC.
In the outskirts of the SMC, the metallicity distribution of the youngest stars ($\textrm{age} < 2~\textrm{Gyr}$) has a peak around $\feh \sim -1$ and a spread of $\sigma_{\feh} \sim 0.2~\textrm{dex}$, which at least means that the metallicity of \clustername\ ($\feh \approx -1.1$) is consistent with young SMC stars \citep{Dobbie:2014}.
